---
title       : Introduction for Brief information of 50 states of the USA
subtitle    : A simple shiny application
author      : Daopeng Shi
job         : Serviceman
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview

Brief information of 50 states of the USA is a very simple shiny application which can be used to get some basic informations about 50 USA states. The information include the specific location of a state on the USA map and some statistics figures of the state based on R maps package and R state.x77 dataset respectively.

You can visit the shiny application by the link:
[Visit Brief information of 50 states of the USA!](https://shidaopeng.shinyapps.io/shinyapp/)

--- .class #id 

## Information UI:  map

```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=4}
require(maps)
par(mfrow=c(1,2))
map("state.vbm", fill = FALSE)
map("state.vbm", fill = FALSE)
map("state.vbm", regions = "California", 
            fill = TRUE, add = TRUE, col = "blue")
par(mfrow=c(1,1))
```

The information UI of map is as above:
* The left figure shows when non of a specific state is chosen from the select box.
* The right figure show when a specific state is chosen(In the figure, California
is chosen). The chosen state will be showed in blue to highlight the location of
the state.

---

## Information UI:  datatable

```{r, echo=FALSE, comment=""}
options(width = 80)
data <- as.data.frame(state.x77)
data <- cbind(Statename = rownames(data), data)
rownames(data)<-NULL
head(data, 5, addrownums = FALSE)
```

Above is the display of detail information of state when non of a specific state
is chosen from the select box(You can also uncheck the check box to hide the 
detail information). The default length of the information is 5 rows(Can be 
adjusted through the shiny datatable). 
```{r ,echo=FALSE, comment=""}
options(width = 80)
data[data$Statename=="California",]
```

When a specific state is chosen, the display of detail information of state is 
as above.

--- &checkbox

## Little quiz

Which of following information about states of the USA can you get from 
application?

1. _Location of state(s) on map of the USA_
2. _Pupulation of state(s)_
3. _Area of state(s)_

*** .hint
Please refer page 3 and 4 of this presentation.

*** .explanation
All the choices are right.

Thank you to use this application. May you have a better understand of the states
of the United States of America.